---
title: "R/Docker Installation Testing"
output: html_document
author: "Simon Bond"
date:  "`r format(Sys.Date(),'%d %b %Y')`" 
---

# Background

R is an open source and free software environment for statistical computing and graphics.
It can be readily downloaded from <http://cran.ma.imperial.ac.uk/> or other mirror sites.
A position paper on its ability to meet FDA and EME regulatory requirements for Clinical Trials  is provided in the R-FDA.pdf appendix and the R-SDLC.pdf gives an overview of the development cycle.
Internal tools are provided to check that an installation is successful. These function by running pre-written scripts to a) check that they run without errors b) the output that is produced matches up to pre-saved output files supplied with the download.

<https://cran.ma.imperial.ac.uk/doc/manuals/r-release/R-admin.html#Testing-a-Unix_002dalike-Installation>

# R System

Local CRSid: `r Sys.getenv("CRSID")`

```{r system}
R.version
Sys.info()
```


```{r config }
knitr::opts_chunk$set(echo = TRUE, warning=TRUE, results = "asis", error = TRUE, message=TRUE,
                      fig.keep = "none"
                      )
base_dir <- file.path(R.home(), "tests","base_tests")
recommended_dir <- file.path(R.home(), "tests","recommended_tests")
#unlink("home_tests",recursive = TRUE, force = TRUE)
unlink(base_dir,recursive = TRUE)
unlink(recommended_dir,recursive = TRUE)
#dir.create("home_tests")
dir.create(base_dir)
dir.create(recommended_dir)
```

Running the installation tests as per the manual

```{r tests, eval=FALSE}
Sys.setenv(LC_COLLATE = "C", LC_TIME="C", LANGUAGE = "en")
success_basic <- tools::testInstalledBasic("both")
success_internet <- tools::testInstalledBasic("internet")
success_base <- tools::testInstalledPackages(scope = "base", 
                                             outDir =base_dir,
                                             errorsAreFatal=FALSE)

if(success_base){
  tools::testInstalledPackages(scope = "base", 
                                             outDir =base_dir,
                                             errorsAreFatal=TRUE)
}

success_recommended <- tools::testInstalledPackages(scope = "recommended", 
                                                    outDir =recommended_dir, 
                                                    errorsAreFatal = FALSE)
if(success_recommended){
  #only run if have fails to see where it happens
  tools::testInstalledPackages(scope = "recommended", 
                                             outDir =recommended_dir,
                                             errorsAreFatal=TRUE)
}



system("rm -rf home_tests")
test_dir <- paste0(R.home(),"/tests")
cmd <- paste("cp -r ", test_dir, " home_tests")
system(cmd)
dir.create("package")
```

The return code from the  tests,  0/1 indicates success/fail.  The outputs and comparisons from each is in the directory "home_tests"

* basic_tests  -  `r success_basic`
* basic internet tests - `r success_internet`
* base_tests - `r success_base`
* recommended_tests - `r success_recommended`


# Non-standard packages

We use a variety of extra packages that need to be tested individually. These rely on a set of test code however, this is not installed by default on Rocker, as it increases the size of images and will only be used once here for UAT.  So in most cases we have to re-download the package to get a copy of the test files, and then use a slightly modified version of tools::testInstalledPackage (where it looks to find the test path). An exception is the in-house cctu package, where we do keep the test files in rocker.

## CCTU

```{r cctutest}
source("test_pkg.R")
unlink("package/cctu")
dir.create("package/cctu")
out <- tools::testInstalledPackage("cctu", outDir="package/cctu",
                                   type= c("examples", "tests")
                                   )
#needs rms installed to pass tests
print(out)
```


```{r packages }
pkgs <- installed.packages()
pkg_list <- pkgs[pkgs[,"LibPath"]=="/usr/local/lib/R/site-library","Package"]
pkg_list <- grep("cctu", pkg_list, value = TRUE, invert=TRUE)
long_hand <- lapply( pkg_list, function(pkg){ knitr::knit_expand("package_validate.Rmd")})
```



`r knitr::knit_child(text=unlist(long_hand))`
